Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-25 paper/ijcai/paper.tex
caption fixed and table percentages

Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project. The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes. Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%  & 22 & 81.48\% & 23 & 85.19\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.05\% & 30 & 78.95\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table*}

>>>>

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of versions where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report}
  \label{table:fsws}
\end{table*}
